Improving the prospects for multimessenger astronomy with \earlywarning\ detection of compact binary coalescence.

### 2011-05-30 figures/diagram.tex
Removed whitener
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@776 ccdd05d5-56c1-461a-bf98-85f6876523b4

		\node[junction] at ($0.5*(u0) + 0.5*(u2) - (0.5, 0)$) (in\x tee) {};
		\node[resample, left=1.75cm of in\x tee] (in\x) {\tiny$\downarrow$};

@@

@@

	\node[draw, left=0.5cm of in0] (whiten) {\emph{whiten}};
	\node[signal, label=left:$x$, label=below:{\small 16384 Hz}, left=0.75cm of whiten] (x) {};
	\node[below=1.5cm of in1] (ellip) {$\vdots$};
	\node[right=1.6cm of ellip] {$\vdots$};
	\node[right=4.1cm of ellip] {$\vdots$};
	\node[above=1mm of out3] {\vdots};
	\draw[->] (x) -- (whiten);
	\draw[->] (whiten) -- (in0);
	\draw[->] (in0) -- (in1);
	\draw (in1) -- (ellip);
	\draw[->] (ellip) -- (in2);

@@

	\node[above=0.5cm of ortho0,align=center] (fir label) {Orthogonal \\ FIR filters \\ $\overbrace{\hspace{1cm}}^{}$};
	\node[right=0.1cm of fir label,align=center] {Reconstruction \\ matrices \\ $\overbrace{\hspace{2.75cm}}^{}$};
	\node[right=3.5cm of fir label,align=center] {Upsampling and \\ SNR accumulation \\ $\overbrace{\hspace{2.75cm}}^{}$};
	\node[left=0.1cm of fir label,align=center] {Down-\\ sampling \\ $\overbrace{\hspace{1cm}}^{}$};
	\node[left=1.75cm of fir label,align=center] {Data acquisition \\ and whitening \\ $\overbrace{\hspace{2cm}}^{}$};

>>>>

		\node[junction] at ($0.5*(u0) + 0.5*(u2) - (0.5, 0)$) (in\x tee) {};

@@

	\node[junction, left=1.9cm of in0tee] (in0) {};
	\node[resample, left=1.75cm of in1tee] (in1) {\tiny$\downarrow$};
	\node[resample, left=1.75cm of in2tee] (in2) {\tiny$\downarrow$};

@@

	\node[signal, label=left:$x$, left=0.75cm of in0] (x) {};
	%\node[draw, left=0.5cm of in0] (whiten) {\emph{whiten}};
	%\node[signal, label=left:$x$, label=below:{\small 16384 Hz}, left=0.75cm of whiten] (x) {};
	\node[below=1.5cm of in1] (ellip) {$\vdots$};
	\node[right=1.6cm of ellip] {$\vdots$};
	\node[right=4.1cm of ellip] {$\vdots$};
	\node[above=1mm of out3] {\vdots};
	\draw[->] (x) -- (in0);
	%\draw[->] (x) -- (whiten);
	%\draw[->] (whiten) -- (in0);
	\draw[->] (in0) -- (in1);
	\draw (in1) -- (ellip);
	\draw[->] (ellip) -- (in2);

@@

	\node[above=0.5cm of ortho0,align=center] (fir label) {Orthogonal \\ FIR filters \\ $\overbrace{\hspace{1cm}}^{}$};
	\node[right=0.1cm of fir label,align=center] {Reconstruction \\ matrices \\ $\overbrace{\hspace{2.75cm}}^{}$};
	\node[right=3.5cm of fir label,align=center] {Interpolation and \\ SNR accumulation \\ $\overbrace{\hspace{2.75cm}}^{}$};
	\node[left=0.3cm of fir label,align=center] {Decimation \\ of input \\ $\overbrace{\hspace{1cm}}^{}$};
	%\node[left=1.75cm of fir label,align=center] {Data acquisition \\ and whitening \\ $\overbrace{\hspace{2cm}}^{}$};
